A Gentle Introduction to Structural Causal Models

### 2021-05-16 scm.Rmd
scm structure

# History

* Path Analysis -> SEM -> SCM
*

# How to build a SCM

@@

- Flexible simulations for higher order problems (intervention, counterfactual)
- Graphical visualization via directed acyclic graph
-

- conflict whether to use graphs or not 
* A SEM is a parametric specification used in applied sciences (parameters contested)
* A Bayesian causal network is another popular causal model using conditional probabilities and NO functions 
* Differences in performance between BCN and SCM

# Performance Evaluation

@@

@@

# Causality -In Between Physical and Social Sciences

>>>>

@@

@@

Consists of graph and assignments: 
Baseline:

$$C:= N_c$$
$$E:=f_E(C,N_E)$$

source: @peters_elements_2017

- Flexible simulations for higher order problems (intervention, counterfactual)
- Graphical visualization via directed acyclic graph

# Comparative Causal Tools

# Historical Development

* Path Analysis -> SEM -> SCM

- conflict whether to use graphs or not 
* A SEM is a parametric specification used in applied sciences (parameters contested)
* A Bayesian causal network is another popular causal model using conditional probabilities and NO functions 
* Differences in performance between BCN and SCM# Performance Evaluation

# Implications

@@
